\section{Features}
\label{Features}

\phantomsection{}
\label{Alpine Package Keeper}
\addcontentsline{toc}{subsection}{Alpine Package Keeper}
\begin{baseBoxThree}{\sL{Alpine Package Keeper}}{dark}
    \bigskip
    The Alpine Package Keeper, commonly referred to as \sTE{apk}, is the package management system used by Alpine Linux.
    It is designed to be lightweight, fast, and efficient, making it well-suited for resource-constrained environments like containers and embedded systems.
    \bigskip
    \begin{baseBoxThree}{Key Features of apk}{dark}
        \smallskip
        \begin{posnexItemize} 
            \item[\sA] \sE{Lightweight}: apk is designed with minimalism in mind, ensuring a small footprint while providing powerful package management capabilities.
            \item[\sA] \sE{Fast and Efficient}: apk operates quickly, making package installation, updates, and removal tasks swift and efficient.
            \item[\sA] \sE{Dependencies Management}: Handles package dependencies automatically, ensuring that all necessary dependencies are installed, updated, or removed as needed.
            \item[\sA] \sE{Security}: Supports digital signatures for packages, ensuring the integrity and authenticity of the software.
            \item[\sA] \sE{Repositories}: Provides access to a wide range of software repositories, allowing users to install a diverse set of packages.
            \item[\sA] \sE{Simplicity}: apk commands are straightforward and easy to use, making it accessible even for those new to Alpine Linux.
        \end{posnexItemize}
        \smallskip
    \end{baseBoxThree}
    \smallskip
    \begin{baseBoxThree}{\gAL{width=1cm}}{dark}
        \begin{posnex}
apk update && apk upgrade
        \end{posnex}
    \end{baseBoxThree}
    \smallskip
\end{baseBoxThree}
